site_map

### 2020-04-20 SST_patterns.Rmd
update

@@

load("Data/OISST_final.RData")
load("Data/G1SST_final.RData")
#load("Data/SACTN_upwell_base.RData")
load("Data/MUR_final.RData")
load("Data/CMC_final.RData")

@@

metrics <- metric_4years %>% 
  mutate(year = year(date_start)) %>% 
  group_by(product, site) %>% 
  summarise(y = n(),
            mean_intensity = mean(intensity_mean),
            mean_dur = mean(duration),
            mean_cumIn = mean(intensity_cumulative)) %>% 
  rename(count = y)
```

>>>>

```{r}
load("Data/site_list_sub.Rdata")
load("Data/SACTN_US.RData")
load("Data/site_pixels.RData") # 5 decimal places
load("Data/OISST.RData") # 2 decimal places
OISST <- BC_avhrr_only_v2_Document_Document 
rm(BC_avhrr_only_v2_Document_Document ); gc()
load("Data/CMC.RData") # 1decimal places
load("Data/MUR.RData")

# ### The temperature products
# load("~/Documents/Upwelling_MCS/Data/Final_G1SST.RData") #G1SST
# load("~/Documents/Upwelling_MCS/Data/Final.RData") # MUR
# load("~/Documents/Upwelling_MCS/Data/SACTN_US.RData") # SACTN
# load("~/Documents/Upwelling_MCS/Data/OISST_sites.RData") # OISST
# load("~/Documents/Upwelling_MCS/Data/CMC_SST.RData") # CMC temperature
```

@@

load("Data/OISST_final.RData")
load("Data/G1SST_final.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_final.RData")
load("Data/CMC_final.RData")
SACTN_upwell_base <- SACTN_upwell_base %>% 
  mutate(product = "SACTN")

### The temperature products
load("~/Documents/Upwelling_MCS/Data/Final_G1SST.RData") #G1SST
load("~/Documents/Upwelling_MCS/Data/Final.RData") # MUR
load("~/Documents/Upwelling_MCS/Data/SACTN_US.RData") # SACTN
load("~/Documents/Upwelling_MCS/Data/OISST_sites.RData") # OISST
load("~/Documents/Upwelling_MCS/Data/CMC_SST.RData") # CMC temperature

@@

SACTN <- SACTN_upwell_base %>% 
   filter(year(date_start) %in% 2011:2014)

metrics <- metric_4years %>% 
  mutate(year = year(date_start)) %>% 
  group_by(product, site) %>% 
  summarise(y = n(),
            mean_intensity = mean(intensity_mean),
            mean_dur = mean(duration),
            mean_cumIn = mean(intensity_cumulative)) %>% 
  rename(count = y)

## Creating a time series graph with all of the products but showing the temperature drop but with no CMC
# X-axis: Date, Y axis: Temp

CMC_temp <- CMC %>% 
  filter(site == "Lamberts Bay",
         year(date) == 2014) %>% 
  dplyr::rename(temp = temp_CMC) %>% 
  mutate(product = "CMC") %>% 
  dplyr::select(date,site,lat,lon,temp,product)#%>% 
 # select(date,site,product,lat,lon,temp)

OISST_temp <- OISST_sites %>% 
  filter(site == "Lamberts Bay",
         year(date)== 2014)%>% 
  mutate(product = "OISST")%>% 
  dplyr::select(date,site,lat,lon,temp,product)

# SACTN_temp <- SACTN_US %>% 
#   filter(site == "Lamberts Bay",
#          year(date) == 2014)%>% 
#   mutate(product = "SACTN") %>% 
#   dplyr::select(date,site,lat,lon,temp,product)

MUR_temp <- Final %>% 
  filter(site == "Lamberts Bay",
         year(date) == 2013)%>% 
  mutate(product = "MUR")%>% 
  dplyr::select(date,site,lat,lon,temp,product)

G1SST_temp <- Final_G1SST %>% 
  filter(site == "Lamberts Bay",
         year(date) == 2014) %>% 
  mutate(product = "G1SST")%>% 
  dplyr::select(date,site,lat,lon,temp,product)

combined_SST <- rbind(CMC_temp,MUR_temp,G1SST_temp,OISST_temp)

ggplot(combined_SST, aes(x = date, y = temp, colour = product)) + 
  geom_line()

### 2020-04-20 site_map.Rmd
update

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + 
  #geom_raster(data = OISST, aes(x = lon, y = lat, fill = temp)) +
   geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group),
                fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 2) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "black", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub, aes(x = lon, y = lat, label = site), 
                     size = 4, box.padding = 2, nudge_x = 0.7, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
  coord_equal(xlim = c(15, 21.5), ylim = c(-35,-27), expand = 0) +
  # geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
  #           alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  # scale_x_continuous(limits = sa_lons, expand = c(0, 0), breaks = seq(15, 35, 5)) +
  # scale_y_continuous(limits = sa_lats, expand = c(0, 0), breaks = seq(-35, -30, 5)) +
  # scale_fill_viridis(
  #   option = "magma",
  #   name = "Temperature (°C)",
  #   alpha = 0.8) +
  xlab("") + ylab("") +
  # annotate("text", label = "INDIAN\nOCEAN", x = 32.00, y = -35.0,
  #            size = 4, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 16, y = -31.5,
             size =5, angle = 0, colour = "black") +
    # annotate("text", label = "Benguela", x = 15, y = -30,
    #          size = 5, angle = 302, colour = "black") +
    # annotate("text", label = "Agulhas", x = 31.7, y = -31.7,
    #          size = 5, angle = 50, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_x_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°S", sep = "")) +
  theme(axis.text = element_text(size = rel(1.2), colour = "black"),
        axis.text.x = element_text(vjust = 1),
        axis.text.y = element_text(hjust = 1),
        axis.title.x = element_text(vjust = 0),
        axis.title.y = element_text(angle = 90, vjust = 0.3),
        axis.ticks = element_line(colour = "black"),
        axis.ticks.length = unit(0.15, "cm"),
        panel.background = element_rect(fill = "white", colour = "black", size = 0.5),
        #panel.border = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=2),
        #(colour =" black"),
        panel.grid.major.x = element_blank(),
        #panel.grid.major.y = element_line(linetype = "dotted", size = 0.2, colour = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        #panel.margin = unit(0.25, "lines"),
        strip.text = element_text(size = rel(1.0)),
        strip.background = element_rect(fill = "white", colour = NA),
        strip.text.x = element_text(),
        strip.text.y = element_text(angle = -90),        
        plot.background = element_rect(colour = "white"),
        plot.title = element_text(size = rel(1.2), vjust = 1),
        plot.margin = unit(c(1, 1, 0.5, 0.5), "lines"))

>>>>

site_map <- ggplot(data = south_africa_coast, aes(x = lon, y = lat)) + 
  #geom_raster(data = OISST, aes(x = lon, y = lat, fill = temp)) +
   geom_polygon(data = south_africa_coast, aes(x = lon, y = lat, group = group),
                fill = "grey", colour = "grey", size = 0.1, show.legend = FALSE) +
  geom_point(data = site_list_sub, aes(x = lon, y = lat), alpha = 0.8, size = 2) +
  geom_point(data = site_pixels, aes(x = lon, y = lat), colour = "black", shape = 0, alpha = 0.8, size = 2.1) +
  geom_label_repel(data =site_list_sub, aes(x = lon, y = lat, label = site), 
                     size = 4, box.padding = 2, nudge_x = 0.7, nudge_y = 0.2, 
                     segment.alpha = 0.4, force = 0.1) +
  coord_equal(xlim = c(15.5, 20), ylim = c(-35,-27), expand = 0) +
  # geom_rect(data = bbox, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
  #           alpha = 0.4, colour = "red", size = 0.1, linetype = 1) +
  # scale_x_continuous(limits = sa_lons, expand = c(0, 0), breaks = seq(15, 35, 5)) +
  # scale_y_continuous(limits = sa_lats, expand = c(0, 0), breaks = seq(-35, -30, 5)) +
  # scale_fill_viridis(
  #   option = "magma",
  #   name = "Temperature (°C)",
  #   alpha = 0.8) +
  xlab("") + ylab("") +
  # annotate("text", label = "INDIAN\nOCEAN", x = 32.00, y = -35.0,
  #            size = 4, angle = 0, colour = "black") +
    annotate("text", label = "ATLANTIC\nOCEAN", x = 16, y = -31.5,
             size =5, angle = 0, colour = "black") +
    # annotate("text", label = "Benguela", x = 15, y = -30,
    #          size = 5, angle = 302, colour = "black") +
    # annotate("text", label = "Agulhas", x = 31.7, y = -31.7,
    #          size = 5, angle = 50, colour = "black") +
  guides(fill = guide_colourbar()) +
  scale_x_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°E", sep = "")) +
    scale_y_continuous(expand = c(0, 0),
                       labels = scales::unit_format(unit = "°S", sep = "")) +
  coord_fixed(ratio = 1, xlim = c(15, 21.5), ylim = c(-35,-27),
                expand = TRUE) +
  theme(axis.text = element_text(size = rel(1.2), colour = "black"),
        axis.text.x = element_text(vjust = 1),
        axis.text.y = element_text(hjust = 1),
        axis.title.x = element_text(vjust = 0),
        axis.title.y = element_text(angle = 90, vjust = 0.3),
        axis.ticks = element_line(colour = "black"),
        axis.ticks.length = unit(0.15, "cm"),
        axis.ticks.margin = unit(0.1, "cm"),
        panel.background = element_rect(fill = "white", colour = "black", size = 0.5),
        #panel.border = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size=2),
        #(colour =" black"),
        panel.grid.major.x = element_blank(),
        #panel.grid.major.y = element_line(linetype = "dotted", size = 0.2, colour = "black"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor = element_blank(),
        #panel.margin = unit(0.25, "lines"),
        strip.text = element_text(size = rel(1.0)),
        strip.background = element_rect(fill = "white", colour = NA),
        strip.text.x = element_text(),
        strip.text.y = element_text(angle = -90),        
        plot.background = element_rect(colour = "white"),
        plot.title = element_text(size = rel(1.2), vjust = 1),
        plot.margin = unit(c(1, 1, 0.5, 0.5), "lines"))
